Actuator line modeling of vertical-axis turbines

### 2016-04-29 paper.tex
Add word 'experiments'

Both the high solidity UNH-RVAT and medium-low solidity RM2 turbines were
modeled using the ALM inside a Reynolds-averaged Navier--Stokes (RANS)
simulation, closed with the standard $k$--$\epsilon$ turbulence model. These
rotors provide diverse parameters, which helped evaluate the robustness of the
ALM. The simulations were performed inside a domain similar in size to that used
in Chapter~\ref{chap:CFD} to mimic the tow tank (3.66 m wide, 2.44 m tall, 1.52
m upstream and 2.16 m downstream), with similar boundary conditions (1 m/s
inflow, no-slip walls and bottom, and a rigid slip for the top). Simulations
were run for a total of 6 seconds, with the latter half used to calculate
performance and wake statistics. Pressure--velocity coupling for the momentum
equation was achieved using the PISO (pressure implicit splitting of operators)
method. A slice of the mesh in the $x$--$y$ plane is shown in
Figure~\ref{fig:ALM-mesh}.

>>>>

Both the high solidity UNH-RVAT and medium-low solidity RM2 turbines were
modeled using the ALM inside a Reynolds-averaged Navier--Stokes (RANS)
simulation, closed with the standard $k$--$\epsilon$ turbulence model. These
rotors provide diverse parameters, which helped evaluate the robustness of the
ALM. The simulations were performed inside a domain similar in size to that used
in Chapter~\ref{chap:CFD} to mimic the tow tank experiments (3.66 m wide, 2.44 m
tall, 1.52 m upstream and 2.16 m downstream), with similar velocity boundary
conditions: 1 m/s inflow, no-slip (fixed to 1 m/s) walls and bottom, and a rigid
slip condition for the top, to approximate some effects of the tow tank's free
surface. Simulations were run for a total of 6 seconds, with the latter half
used to calculate performance and wake statistics. Pressure--velocity coupling
for the momentum equation was achieved using the PISO (pressure implicit
splitting of operators) method. A slice of the mesh in the $x$--$y$ plane is
shown in Figure~\ref{fig:ALM-mesh}.
